DeepSphere: a graph-based spherical CNN

### 2019-09-25 main.tex
Updates from Overleaf

Graphs are built with \eqnref{weights:belkin}, $k = 8, 20, 40$ neighbors, and the corresponding optimal kernel widths $t$ given in \secref{optimal}.
Following \citet{perraudin2019deepspherecosmo}, the NN is made of $6$ graph convolutional layers, each followed by a max pooling layer which down-samples by $4$.
A GAP and softmax follow.
The polynomials are all of order $K=5$ and the number of channels per layer is $16, 32, 64, 64, 64, 2$, respectively.
The cross-entropy loss is optimized with Adam for 80 epochs.
The learning rate is $2 \cdot 10^{-4} \cdot 0.999^{\textrm{step}}$ and the batch size is 8.

@@

Leveraging these three operators \cite{belkin2005towards, belkin2007convergence} have build proofs of both pointwise and spectral convergence of the extended graph Laplacian towards the Laplace-Beltrami operator in the general setting of any compact, closed and infinitely differentiable maniform $\mathcal M$ where the sampling scheme $\V$ is drawn at random on the manifold. For this reason, their results are all to be interpreted in a probabilistic sense.
Their proofs consist in establishing that \eqref{eq:Heat Kernel Graph Laplacian operator} converges in probability towards \eqref{eq:Functional approximation to the Laplace-Beltrami operator} as $n\rightarrow \infty$ and \eqref{eq:Functional approximation to the Laplace-Beltrami operator} converges toward \eqref{eq:laplace-beltrami} as $t\rightarrow 0$. In particular, this second step is given by the following:
\begin{prop}
[\cite{belkin2005towards}, Proposition 4.4]
Let $\mathcal{M}$ be a $k$-dimensional compact smooth manifold embedded in some Euclidean space $\mathbb{R}^N$, and fix $y\in\mathcal{M}$. Let $f\in\mathcal{C}_\infty(\mathcal{M)}$. Then
\begin{equation}
\frac{1}{t}\frac{1}{(4\pi t)^{k/2}} L^tf(y) \xrightarrow{t\to 0 } \frac{1}{\text{vol}(\mathcal M)}\Delta_{\mathcal M}f(y).
\end{equation}
\label{prop:3}
\end{prop}

\paragraph{Building the proof.}
As the sphere is a compact smooth manifold embedded in $\mathbb{R}^3$, we can reuse proposition \ref{prop:3}. Thus, our strategy to prove Theorem \ref{theo:pointwise convergence for a regular sampling} is to a) show that
\begin{equation}\label{eq:continuous convergence}
 \lim_{n\to\infty}L_n^{t} f(y) =  L^t(y)
\end{equation}
for a particular class of sampling and b) apply Proposition \ref{prop:3}.

@@

We start by proving that for smooth functions, the sum converges toward an integral as the sampling increase in size.
\begin{prop}\label{prop:1}
	For an equal area sampling $\{x_i\in\S^2\}_{i=0}^{n-1}: A_i=A_j \forall i,j$ of the sphere it is true that for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance $\|\cdot\|$ with Lipschitz constant $C_f$
	\begin{equation*}
	\left| \int_{\S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right|\leq C_f d^{(n)}.	    
	\end{equation*}
	Furthermore, for all $y\in\S^2$ the Heat Kernel Graph Laplacian operator $L^t_n$ converges pointwise to the functional approximation of the Laplace Beltrami operator $L^t$
	\begin{equation*}
	 L_n^tf(y)\xrightarrow{n\to\infty} L^tf(y).
	\end{equation*}
\end{prop}
\begin{proof}

@@

\nati{@martino, actually we do not need $ d^{(n)}\leq \frac{1}{\sqrt{n}}$, we only need $ d^{(n)}\leq \frac{1}{n^\alpha}$, where $\alpha>0$. As the $\S^2$ is of dimension $2$, $\alpha$ cannot be larger than $\linefrac{1}{2}$. If we put that into the theorem, we obtain that $\frac{5}{2}\beta+\alpha>0 \iff \beta>-\frac{2\alpha}{5}$. I think this is important, because we can still have convergence even if we do not have perfect patches... Please confirm ASAP, so we can update the Proposition and the text bellow. For HealPix sampling, we could say that while we have not proof, it make sense that it statisfies the hypothesis probably with $\alpha=\linefrac{1}{2}$.}

>>>>

Graphs are built with \eqnref{weights:belkin}, $k = 8, 20, 40$ neighbors, and the corresponding optimal kernel widths $t$ given in \secref{optimal}.
Following \citet{perraudin2019deepspherecosmo}, the NN is made of $5$ graph convolutional layers, each followed by a max pooling layer which down-samples by $4$.
A GAP and a fully connected layer with softmax follow.
The polynomials are all of order $K=5$ and the number of channels per layer is $16, 32, 64, 64, 64$, respectively.
The cross-entropy loss is optimized with Adam for 80 epochs.
The learning rate is $2 \cdot 10^{-4} \cdot 0.999^{\textrm{step}}$ and the batch size is 8.

@@

Leveraging these three operators \cite{belkin2005towards, belkin2007convergence} have build proofs of both pointwise and spectral convergence of the extended graph Laplacian towards the Laplace-Beltrami operator in the general setting of any compact, closed and infinitely differentiable maniform $\mathcal M$, where the sampling scheme $\V$ is drawn randomly on the manifold. For this reason, their results are all to be interpreted in a probabilistic sense.
Their proofs consist in establishing that \eqref{eq:Heat Kernel Graph Laplacian operator} converges in probability towards \eqref{eq:Functional approximation to the Laplace-Beltrami operator} as $n\rightarrow \infty$ and \eqref{eq:Functional approximation to the Laplace-Beltrami operator} converges toward \eqref{eq:laplace-beltrami} as $t\rightarrow 0$. In particular, this second step is given by the following:
\begin{prop}
[\cite{belkin2005towards}, Proposition 4.4]
Let $\mathcal{M}$ be a $k$-dimensional compact smooth manifold embedded in some Euclidean space $\mathbb{R}^N$, and fix $y\in\mathcal{M}$. Let $f\in\mathcal{C}_\infty(\mathcal{M)}$. Then
\begin{equation}
\frac{1}{t}\frac{1}{(4\pi t)^{k/2}} L^tf(y) \xrightarrow{t\to 0 } \frac{1}{\text{vol}(\mathcal M)}\Delta_{\mathcal M}f(y).
\end{equation}
\label{prop:3}
\end{prop}

\paragraph{Building the proof.}
As the sphere is a compact smooth manifold embedded in $\mathbb{R}^3$, we can reuse proposition \ref{prop:3}. Thus, our strategy to prove Theorem \ref{theo:pointwise convergence for a regular sampling} is to a) show that
\begin{equation}\label{eq:continuous convergence}
 \lim_{n\to\infty}L_n^{t} f(y) =  L^t(y)
\end{equation}
for a particular class of \emph{deterministic} sampling schemes and b) apply Proposition \ref{prop:3}.

@@

We start by proving that for smooth functions, for any fixed $t$, the extended graph Laplacian $L^t_n$ converges towards its continuous counterpart $L^t$ as the sampling increases in size.
\begin{prop}\label{prop:1}
	For an equal area sampling $\{x_i\in\S^2\}_{i=0}^{n-1}: A_i=A_j \forall i,j$ of the sphere it is true that for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance $\|\cdot\|$ with Lipschitz constant $C_f$
	\begin{equation*}
	\left| \int_{\S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right|\leq C_f d^{(n)}.	    
	\end{equation*}
	Furthermore, for all $y\in\S^2$ the Heat Kernel Graph Laplacian operator $L^t_n$ converges pointwise to the functional approximation of the Laplace Beltrami operator $L^t$
	\begin{equation*}
	 L_n^tf(y)\xrightarrow{n\to\infty} L^tf(y).
	\end{equation*}
\end{prop}
\begin{proof}

@@

% I don't really have time 
% \nati{@martino, actually we do not need $ d^{(n)}\leq \frac{1}{\sqrt{n}}$, we only need $ d^{(n)}\leq \frac{1}{n^\alpha}$, where $\alpha>0$. As the $\S^2$ is of dimension $2$, $\alpha$ cannot be larger than $\linefrac{1}{2}$. If we put that into the theorem, we obtain that $\frac{5}{2}\beta+\alpha>0 \iff \beta>-\frac{2\alpha}{5}$. I think this is important, because we can still have convergence even if we do not have perfect patches... Please confirm ASAP, so we can update the Proposition and the text bellow. For HealPix sampling, we could say that while we have not proof, it make sense that it statisfies the hypothesis probably with $\alpha=\linefrac{1}{2}$.}
